%-------------------------
% Jake's Resume Template
% Wu-Hung Hsiao — converted from Onepage resume v2
%-------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{newtxtext}   % Times New Roman
\usepackage[T1]{fontenc}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-4pt}\bfseries\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingTwo}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Wu-Hung Hsiao} \\ \vspace{1pt}
    \small
    \faPhone\ +1 339-226-2664 $|$
    \href{mailto:hsiao.wu@northeastern.edu}{\faEnvelope\ hsiao.wu@northeastern.edu} $|$
    \faMapMarker\ Boston, MA
\end{center}

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Northeastern University}{Boston, MA}
      {Master of Science in Cybersecurity}{Sep 2025 -- Present}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Intensive CS, Discrete Structures, Software Security, Cybersecurity Defenses}
      \resumeItemListEnd
    \resumeSubheading
      {University of Minnesota, Twin Cities}{Minneapolis, MN}
      {Bachelor of Arts in Economics}{Dec 2020}
      \resumeItemListStart
        \resumeItem{\textbf{Coursework:} Econometrics, Regression Analysis, Computer Science Fundamentals (Python)}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Professional Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Unition Technology}{Taipei City, Taiwan}
      {Software Development Engineer}{Oct 2022 -- Aug 2025}
      \resumeItemListStart
        \resumeItem{Scaled transaction capacity to 24M+ daily and achieved 99.9\% uptime by optimizing ASP.NET Core and SQL indexing.}
        \resumeItem{Reduced maintenance overhead by 80\% by building a centralized real-time operations dashboard for non-technical staff.}
        \resumeItem{Boosted productivity by 30\% by spearheading company-wide n8n automation training across admin and dev workflows.}
        \resumeItem{Reduced data retrieval latency by 40\% and integrated 5+ game providers by engineering high-performance RESTful APIs.}
        \resumeItem{Slashed regression testing from 3 days to 4 hours and increased QA capacity by 50\% by standardizing automated testing.}
      \resumeItemListEnd

    \resumeSubheading
      {Google (Contractor)}{New Taipei City, Taiwan}
      {Software Test Engineer}{Dec 2020 -- Oct 2022}
      \resumeItemListStart
        \resumeItem{Tripled data labeling throughput and boosted accuracy from 83\% to 99\% by developing Python automation scripts.}
        \resumeItem{Reduced manual testing time by 80\% by engineering Linux shell scripts to automate Android Compliance Tests.}
        \resumeItem{Achieved 100\% on-time delivery of ML training datasets by streamlining the data labeling pipeline and aligning data requirements with ML engineers.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS & CERTIFICATIONS-----------
\section{Technical Skills \& Certifications}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Tools}{: Python, C\#, SQL, Shell Scripting, R, .NET Core, Selenium, ADB, Git, Docker, Jenkins, n8n} \\
     \textbf{Cloud \& Domains}{: Google Cloud Platform (GCP), AWS, CI/CD, Linux, Backend Development, APIs, Test Automation} \\
     \textbf{Certifications (2021--2025)}{: Foundation of Responsible AI $|$ Randomized Algorithms $|$ AWS Cloud IT $|$ Google AI Essentials $|$ Agile with Jira $|$ Google Cloud Fundamentals $|$ Google IT Support $|$ Google Data Analytics}
    }}
 \end{itemize}

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Economic Impact Analysis} $|$ \emph{University Capstone Project $|$ R, Statistical Modeling}}{}
          \resumeItemListStart
            \resumeItem{Advanced data interpretation from raw datasets to validated predictions by building multivariable regression models in R to analyze the impact of education spending on OECD national income.}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Infa} $|$ \emph{Backend Infrastructure Library $|$ C\#, ASP.NET Core, Redis}}{}
          \resumeItemListStart
            \resumeItem{Reduced microservice setup time from days to hours by engineering a centralized .NET library encapsulating Redis and HTTP to accelerate backend development and eliminate code duplication.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
